---
title: "R Notebook"
author: "Connor Toliver; @connortoliver"
output:
  html_document:
    df_print: paged
---

First, let's read in the data.

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco)
```

## \#1.

Let's make a histogram of the rating distribution.
```{r}
hist(choco$Rating)
```

The ratings appear to be skewed slightly left, with the most common ratings being between 2.5 and 3.5. There appear to be some outliers at the high end of the ratings near 4.5 — 5.We can confirm this with a box plot.

```{r}
boxplot(choco$Rating)
```


According to the box plot, there are even some outliers from 1 up to about 2.

## \#2.

Let's see if ratings depend on the cacao percentage of a chocolate bar.

```{r}
plot(choco$Rating, choco$Cocoa.Pct, pch=19)
```

There doesn't appear to be any relationship between cacao percentage and the rating.

## Preliminary exploration for question set in `team.Rmd`
```{r}
#1. What is the overall number of chocolate bars rated?
nrow(choco)

#2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.


#3. Which are the three locations with the most ratings? How do ratings compare across these company locations?
sort(table(choco$Company.Location), decreasing = TRUE)
chocoCountries <- choco[choco$Company.Location == c('U.S.A.', 'France', 'Canada'), ]


```

