---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


```{r}
library(ggplot2)
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
nrow(choco)
```

```{r}
ggplot(choco, aes(x = choco$Review.Date)) + geom_bar()

```

According to the bar chart, there are more ratings in recent years.

```{r}
sort(table(choco$Company.Location), decreasing = TRUE)
```
```{r}
mean(choco$Rating[choco$Company.Location == "U.S.A."])
```
```{r}
mean(choco$Rating[choco$Company.Location == "France"])
```
```{r}
mean(choco$Rating[choco$Company.Location == "Canada"])
```

Canada has the highest average rating out of the three countries but they are all fairly close.

```{r}
ggplot(choco, aes(x=choco$Review.Date, y=choco$Rating)) + geom_point(shape=16, size=3) + theme_bw()
```
We wanted to see if there was a correlation between Review date and Rating and based off this scatterplot it appears that there really isn't any correlation.

We took turns working on questions and pushing and pulling from different laptops. It was an improvement from lab 1. Individual 1 created the github repository and individual 2 cloned it.
